Towards semantic-rich word embeddings

### 2019-04-05 paper/main.tex
Move repository link to footnote
Change "time" to "training epochs" in 5.4
Fix abstract

In recent years, word embeddings have been shown to improve the performance in NLP tasks such as syntactic parsing or sentiment analysis.
While useful, they are problematic in representing ambiguous words with multiple meanings, since they keep a single representation for each word in the vocabulary.
Embeddings of ambiguous words and their meanings (which we call \textit{keywords}) could be useful for solving the Word Sense Disambiguation (WSD) task.

In this work, we present how a word embeddings average-based method can be used to produce semantic-rich keyword and context embeddings, and how the former can be improved with embeddings distance optimization techniques.
We also open-source a small WSD dataset that was created for the purpose of evaluating methods presented in this research.
It is composed of 6 ambiguous words, with 4 to 7 meanings each, and collected real-world usage examples of those meanings, with tagged words to be disambiguated.

@@

Dataset, together with the code to execute experiments from this paper, can be found on our GitHub repository \cite{repository}.

@@

\subsection{Accuracy in time}
\label{sec:exp_epochs}
In previous experiments, we performed only one epoch of training, i.e. we used each training example only once for keyword embeddings optimization.
The goal of this experiment is to check how a number of epochs (full passes through training data) affects the final accuracy.
We run 5 epochs of training, using best parameters from previous experiments: \(l=3, \alpha=0.25, \beta=0.05\) (Fig. \ref{fig:exp4_1_epochs_fixed}).

>>>>

In recent years, word embeddings have been shown to improve the performance in NLP tasks such as syntactic parsing or sentiment analysis.
While useful, they are problematic in representing ambiguous words with multiple meanings, since they keep a single representation for each word in the vocabulary.
Constructing separate embeddings for meanings of ambiguous words could be useful for solving the Word Sense Disambiguation (WSD) task.

In this work, we present how a word embeddings average-based method can be used to produce semantic-rich meaning embeddings, and how they can be improved with distance optimization techniques.
We also open-source a WSD dataset that was created for the purpose of evaluating methods presented in this research.

@@

Dataset, together with the code to execute experiments from this paper, can be found on our GitHub repository\footnote{https://github.com/gberinger/automatic-wiki-links}.

@@

\subsection{Accuracy in training epochs}
\label{sec:exp_epochs}
In previous experiments, we performed only one epoch of training, i.e. we used each training example only once for keyword embeddings optimization.
The goal of this experiment is to check how a number of epochs (full passes through training data) affects the final accuracy.
We run 5 epochs of training, using best parameters from previous experiments: \(l=3, \alpha=0.25, \beta=0.05\) (Fig. \ref{fig:exp4_1_epochs_fixed}).
